No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-10 R/MSE-manuscript.Rmd
Spell check

---
title: 'No Replication Without Process Documentation:  An Assessment of Management
  Strategy Evaluations'
author:
- affiliation: School for Marine Science and Technology, University of Massachusetts
    - Dartmouth
  name: Jonathan W. Cummings, Amanda Hart, Gavin Fay
output:
  bookdown::html_document2:
    number_sections: false
  bookdown::word_document2:
  bookdown::pdf_document2:
    number_sections: false
always_allow_html: yes
biblio-style: apalike
endnote: no
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
header-includes: \usepackage{hyperref}
keywords: pandoc, r markdown, knitr
bibliography: MSEreview.bib
abstract: The aim and vision for fisheries management that comes from management strategy evaluation and adaptive management is a noble and aspirational vision.  We review MSE documentation in the published literature to appraise the achievement of this vision, finding that reality doesn't fully reflect this vision. The steps taken to complete the management strategy evaluation process often are not documented. Scientists often filled the role of fishery stakeholders, seemingly selecting the objectives and alternatives to evaluate in most management strategy evaluations. Facilitators and decision analysts -- participants focused on the decision making process rather than making the decision -- were rarely participants in MSE processes.  Conservation, Economic, and Yield focused objectives were commonly considered in MSE processes, while broader social objectives were rarely considered.  The picture painted by MSE documentation is primarily one of scientist driven simulation studies rather than management driven decision processes, with limited process documentation occurring. We hope providing a repository for reviews of previous management strategy evaluatons will aid and speed learning among practitioners of management strategy evaluation.
---

@@

An incresingly recognized challenge in fisheries management is responding to changes in the productivity of fisheries stocks as a result of climate change [@busch_climate_2016; @brander_global_2007]. We also conduct a focused analysis of MSE processes that address the influence of climate change on fisheries management, highlighting aspects of MSE processes that model climate change as a driver of system status.

@@

```{r MSEcount}
MSE_Type<-c("Published","Random Sample","Climate Change")
Count<-c(154,30,"12*")
Table1.data<-as_tibble(cbind(MSE_Type,Count))
  Table1.data %>%
    rename("MSE Type"=MSE_Type) %>% 
  kable(caption = "Januaray 8, 2019 Web of Science 'management strategy evaluation' search results") %>% 
  kable_styling() %>% 
    add_footnote(c("We also reviewed 4 additional climate change MSE articles published in 2019 for a total of 16."), notation = "symbol")
```

@@

The primary participants and leaders of the MSE processes were scientists, while some MSE process were led by governments and management agencies (Figure \@ref(fig:participants) Process).  Scientists were exlicitly the leaders -- or the sole participants and therefore seemingly the leaders -- in 73 percent of the MSE processes, while 27 percent of processes lacked enough documentation of participants and leadership such that we were unable to identify a presumed leader of the process.

@@

Climate change MSEs were more likely to explicitly document the trade-off analysis stage, equaly likely to document the alternatives stages, but were less likely to document the other stages in the decision process.
```{r, CCstages}
freq.data_CC %>%
  mutate("Percent"=round(Percent,0)) %>% 
  select(Explicit, Percent, Number, -Analysis) %>% 
  kable(caption = "Prevalence of explicit documentation of stages in climate change MSE processes") %>%
  kable_styling()
```

Including climate change in a MSE appears to reduce the complexity of other stages in the MSE process, in particular those stages that utilize input from additional particapants. On average climate change MSEs consider fewer drivers, consider less diverse objectives, and explicitly document fewer stages of the MSE process.  If the MSE process is time, effort, or participant limited the inclusion of climate change may be utlizing time, effort, or outside participants to focus on climate change rather than other aspects of the MSE process.

@@

We found that management strategy evaluations do typically assess the consequences of uncertainty for achieving management goals, but other factors influencing the consequences of management strategies get more sporadic treatment.  Data limitation is a frequent concern in fisheries management, and contributes to the degree of uncertainty present in fisheries management.  Next to accounting for uncertainty, accessing the influence of data quality and availablity, i.e.,  monitoring methodology was the most prevalent driver included in MSEs.  This likely points to a desire for the design and use of cost-effective fisheries monitoring plans, suggesting future MSEs may be able to learn from the set including monitoring methodology as a driver. Additionally, the use of value of information analyses could expand upon the benefits of MSE as a tool to direct scientific resources [@runge_2011; @moore_2012]. While discussions of fisheries research and management seem to be moving toward ecosystem effects, spatial models, and multiple species models, these characteristics were rarely considered in the set of MSEs we reviewed.

>>>>

---
title: 'No Replication Without Process Documentation:  An Assessment of Management
  Strategy Evaluations'
author:
- affiliation: School for Marine Science and Technology, University of Massachusetts
    - Dartmouth
  name: Jonathan W. Cummings, Amanda Hart, Gavin Fay
output:
  bookdown::html_document2:
    number_sections: false
  bookdown::word_document2:
  bookdown::pdf_document2:
    number_sections: false
always_allow_html: yes
biblio-style: apalike
endnote: no
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
header-includes: \usepackage{hyperref}
keywords: pandoc, r markdown, knitr
bibliography: MSEreview.bib
abstract: The aim and vision for fisheries management that comes from management strategy evaluation and adaptive management is a noble and aspirational vision.  We review MSE documentation in the published literature to appraise the achievement of this vision, finding that reality doesn't fully reflect this vision. The steps taken to complete the management strategy evaluation process often are not documented. Scientists often filled the role of fishery stakeholders, seemingly selecting the objectives and alternatives to evaluate in most management strategy evaluations. Facilitators and decision analysts -- participants focused on the decision making process rather than making the decision -- were rarely participants in MSE processes.  Conservation, Economic, and Yield focused objectives were commonly considered in MSE processes, while broader social objectives were rarely considered.  The picture painted by MSE documentation is primarily one of scientist driven simulation studies rather than management driven decision processes, with limited process documentation occurring. We hope providing a repository for reviews of previous management strategy evaluations will aid and speed learning among practitioners of management strategy evaluation.
---

@@

An increasingly recognized challenge in fisheries management is responding to changes in the productivity of fisheries stocks as a result of climate change [@busch_climate_2016; @brander_global_2007]. We also conduct a focused analysis of MSE processes that address the influence of climate change on fisheries management, highlighting aspects of MSE processes that model climate change as a driver of system status.

@@

```{r MSEcount}
MSE_Type<-c("Published","Random Sample","Climate Change")
Count<-c(154,30,"12*")
Table1.data<-as_tibble(cbind(MSE_Type,Count))
  Table1.data %>%
    rename("MSE Type"=MSE_Type) %>% 
  kable(caption = "January 8, 2019 Web of Science 'management strategy evaluation' search results") %>% 
  kable_styling() %>% 
    add_footnote(c("We also reviewed 4 additional climate change MSE articles published in 2019 for a total of 16."), notation = "symbol")
```

@@

The primary participants and leaders of the MSE processes were scientists, while some MSE process were led by governments and management agencies (Figure \@ref(fig:participants) Process).  Scientists were explicitly the leaders -- or the sole participants and therefore seemingly the leaders -- in 73 percent of the MSE processes, while 27 percent of processes lacked enough documentation of participants and leadership such that we were unable to identify a presumed leader of the process.

@@

Climate change MSEs were more likely to explicitly document the trade-off analysis stage, equally likely to document the alternatives stages, but were less likely to document the other stages in the decision process.
```{r, CCstages}
freq.data_CC %>%
  mutate("Percent"=round(Percent,0)) %>% 
  select(Explicit, Percent, Number, -Analysis) %>% 
  kable(caption = "Prevalence of explicit documentation of stages in climate change MSE processes") %>%
  kable_styling()
```

Including climate change in a MSE appears to reduce the complexity of other stages in the MSE process, in particular those stages that utilize input from additional participants. On average climate change MSEs consider fewer drivers, consider less diverse objectives, and explicitly document fewer stages of the MSE process.  If the MSE process is time, effort, or participant limited the inclusion of climate change may be utilizing time, effort, or outside participants to focus on climate change rather than other aspects of the MSE process.

@@

We found that management strategy evaluations do typically assess the consequences of uncertainty for achieving management goals, but other factors influencing the consequences of management strategies get more sporadic treatment.  Data limitation is a frequent concern in fisheries management, and contributes to the degree of uncertainty present in fisheries management.  Next to accounting for uncertainty, accessing the influence of data quality and availability, i.e.,  monitoring methodology was the most prevalent driver included in MSEs.  This likely points to a desire for the design and use of cost-effective fisheries monitoring plans, suggesting future MSEs may be able to learn from the set including monitoring methodology as a driver. Additionally, the use of value of information analyses could expand upon the benefits of MSE as a tool to direct scientific resources [@runge_2011; @moore_2012]. While discussions of fisheries research and management seem to be moving toward ecosystem effects, spatial models, and multiple species models, these characteristics were rarely considered in the set of MSEs we reviewed.
